The Implications of Local Fluctuations in the Galactic Midplane for Dynamical Analysis in the \textit{Gaia} Era

### 2019-07-26 paper/ms.tex
Update short title
Clean up energy argument

\shortauthors{Beane et al.}
\shorttitle{Implications of Disk Oscillations}

@@

\textbf{Because the energies in the radial and vertical coordinates are
related to the radial and vertical actions by a constant
(Equation~\eqref{eq:JR_Jz_epi}), the fractional error in these two energies is
the same as the actions. The energy in the azimuthal coordinate can be readily
computed ($E_{\phi} = \frac{1}{2}v_{\phi}^2$), and we therefore conclude that
the error induced in the total energy is:
\beq\label{eq:error_total_energy}
\frac{\Delta E}{E} = \frac{\Delta J_R}{J_R} + 2\frac{\Delta J_{\phi}}{J_{\phi}}
                     + \frac{\Delta J_z}{J_z}\text{.}
\eeq}

>>>>

\shortauthors{Beane et al.}
\shorttitle{Galactic Dynamical Analysis and Midplane Fluctuations}

@@

\textbf{Because the energies in the radial and vertical coordinates are
related to the radial and vertical actions by a constant
(Equation~\eqref{eq:JR_Jz_epi}), the fractional error in these two energies is
the same as the actions.\footnote{This ignores any potential error in the epicyclic and vertical frequencies.} The energy in the azimuthal coordinate can be readily
computed ($E_{\phi} = \frac{1}{2}v_{\phi}^2$). Using standard propagation of errors, we see that $\Delta E_{\phi}/E_{\phi}$ and $\Delta J_{\phi}/J_{\phi}$ (Equation~\eqref{eq:induced_Jphi}) differ by a $\Delta R/R_g$ term. Since $R_g\approx 8\,\kpc$, we expect this term to be negligible and we therefore conclude that:
\beq\label{eq:error_total_energy}
\frac{\Delta E}{E} \approx \frac{\Delta J_R}{J_R} + 2\frac{\Delta J_{\phi}}{J_{\phi}}
                     + \frac{\Delta J_z}{J_z}\text{.}
\eeq}
